---
title: "DS202_lab3"
author: "Kenneth Mendoza"
date: "October 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,eval=FALSE}
happy <- readRDS("HAPPY.rds")
```

```{r,eval=FALSE}
names(happy) = tolower(names(happy))
```

#1
```{r,eval=FALSE}
happy[ happy == "IAP" ] <- NA #replaces values in PolViews that are "IAP" to NA
happy[ happy == "DK" ] <- NA #replaces values in PolViews that are "DK" to NA
happy[ happy == "NA" ] <- NA #replaces values in PolViews that are "NA" to NA

head(happy, 10)
```






Initial exploration revealed that some data processing was needed before we could proceed with further visualization. All missing values were encoded with 'NA' as follows:
```{r}
library(classdata)
happy[ happy == "IAP" ] <- NA #replaces values in PolViews that are "IAP" to NA
happy[ happy == "DK" ] <- NA #replaces values in PolViews that are "DK" to NA
happy[ happy == "NA" ] <- NA #replaces values in PolViews that are "NA" to NA
sum(is.na(happy)) #finds how many variables were replaced with NA
```
In total there were `36391` number of missing values for the following `7` variables. 










#2
```{r,eval=FALSE}
class(happy$happy)
levels(factor(happy$happy))
```
```{r,eval=FALSE}
class(happy$year)
```
```{r,eval=FALSE}
class(happy$age)
happy[ happy == "89 OR OLDER" ] <- 89
happy$age <- as.numeric(as.character(happy$age))
```

```{r,eval=FALSE}
class(happy$sex)
```

```{r,eval=FALSE}
class(happy$marital)
```

```{r,eval=FALSE}
class(happy$degree)
```

```{r,eval=FALSE}
class(happy$finrela)
```

```{r,eval=FALSE}
class(happy$health)
```

```{r,eval=FALSE}
class(happy$wtssall)
```

```{r,eval=FALSE}
class(happy$partyid)
```

```{r,eval=FALSE}
class(happy$polviews)
```




Variables were also cast into the correct type in order to ease data visualization. This was done by:
```{r}
happy[ happy == "89 OR OLDER" ] <- 89
happy$age <- as.numeric(as.character(happy$age))
class(happy$age)
```
This was done to change age from a character type to a numeric type. The rest of the variables are the correct type.






#3
```{r,eval=FALSE}
library(ggplot2)
unique(happy$happy)
happyhap= happy[order(happy$happy),]
ggplot(happyhap, aes(happy)) + geom_bar()

```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$sex)
happysex = happy[order(happy$sex),]
ggplot(happysex, aes(sex)) + geom_bar()
```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$marital)
happymar= happy[order(happy$marital),]
ggplot(happymar, aes(marital)) + geom_bar()
```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$degree)
happydeg = happy[order(happy$degree),]
ggplot(happydeg, aes(degree)) + geom_bar()
```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$finrela)
happyfin = happy[order(happy$finrela),]
ggplot(happyfin, aes(finrela)) + geom_bar()

```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$health)
happyhealth =happy[order(happy$health),]
ggplot(happyhealth, aes(health)) + geom_bar()

```

```{r,eval=FALSE}
library(ggplot2)
unique(happy$partyid)
happypart = happy[order(happy$partyid),]
ggplot(happypart, aes(partyid)) + geom_bar()
```

```{r,eval=FALSE}
<<<<<<< HEAD
library(ggplot2)
unique(happy$polviews)
happypol = happy[order(happy$polviews),]
ggplot(happypol, aes(polviews)) + geom_bar()
```





```{r,eval=FALSE}
library(ggplot2)
unique(happy$happy)
happyhap= happy[order(happy$happy),]
ggplot(happyhap, aes(happy)) + geom_bar()
```

The following code shows a bar graph for the factors of happiness.

```{r,eval=FALSE}
library(ggplot2)
unique(happy$sex)
happysex = happy[order(happy$sex),]
ggplot(happysex, aes(sex)) + geom_bar()
```

The following code shows a bar graph for the factors of sex.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$marital)
happymar= happy[order(happy$marital),]
ggplot(happymar, aes(marital)) + geom_bar()
```

The following code shows a bar graph for the factors of marital status.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$degree)
happydeg = happy[order(happy$degree),]
ggplot(happydeg, aes(degree)) + geom_bar()
```

The following code shows a bar graph for the factors of the education degree obtained.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$finrela)
happyfin = happy[order(happy$finrela),]
ggplot(happyfin, aes(finrela)) + geom_bar()
```

The following code shows a bar graph for the factors of financial status.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$health)
happyhealth =happy[order(happy$health),]
ggplot(happyhealth, aes(health)) + geom_bar()
```

The following code shows a bar graph for the factors of health status.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$partyid)
happypart = happy[order(happy$partyid),]
ggplot(happypart, aes(partyid)) + geom_bar()
```

The following code shows a bar graph for the factors of party ID.


```{r,eval=FALSE}
library(ggplot2)
unique(happy$polviews)
happypol = happy[order(happy$polviews),]
ggplot(happypol, aes(polviews)) + geom_bar()
```

The following code shows a bar graph for the factors of political views.


##Part 2



```{r}
happy$age <- as.numeric(as.character(happy$age))
ggplot(data = happy, aes(x = age, color = sex)) + geom_histogram(binwidth = 2) + facet_wrap(~sex) + ggtitle("Number of Survey Takers vs Age")

ggplot(data = happy, aes(x = year)) + geom_histogram(binwidth = 5) + facet_wrap(~sex) + ggtitle("Number of People vs Year")
```

```{r}
happy <- happy[complete.cases(happy[, 'happy']), ]

# plot 1

ggplot(data = happy, aes(x = age)) + facet_wrap(~happy) + geom_histogram(binwidth = 1)

#plot 2

ggplot(data = happy, aes(x = degree), stat = 'count') + facet_wrap(~happy) + geom_bar(mapping = aes(fill = degree))
 + coord_flip() + labs(title = "Happiness Based on Degree Obtained")
```

```{r}
# plot 2

```









