---
title: "Team"
author: "Kenneth Mendoza"
date: "September 18, 2019"
output: html_document
---
Joel Von Behren & Kenny Mendoza
https://github.com/kenneh7/ds202_lab2
Kenneh7/DS202_LAB2

```{r, eval=FALSE}
recent_rating = choco[choco$Review.Date>2011,] #Grabs data from choco only if the review date is greater than 2011
unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? 54 countries, 61 levels
recent_rating$Company.Location = droplevels(recent_rating$Company.Location) #drops the extra, unused levels from the data
head(recent_rating) #should output the first data entry for recent_rating
cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location) #creates a table with columns: REview date and Company Location
cross_table #displays table
which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0) #Displays company locations with a cacao review for every year since 2012
france_recent = subset(recent_rating,Company.Location =='France') #creates a subset table, where company location is only in France
uk_recent = subset(recent_rating,Company.Location =='U.K.') #creates a subset table, where company location is only in U.K
germany_recent = subset(recent_rating,Company.Location=='Germany') #creates a subset table, where company location is only in Germany
par(mfrow=c(2,2)) #sets parameters to 2,2
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green') #if the yearly rating is above the median rating, color returns as blue. Else, the color returns as green.
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") #plots the cocoa percent and review date for France. Using the above code "color1" as the colors of the points.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18) #error, new.plot not called, should output a legend at the bottom right. Output would explain colors of points.
color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red')#if the yearly rating is above the median rating, color returns as purple. Else, the color returns as red.
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK")#plots the cocoa percent and review date for UK. Using the above code "color2" as the colors of the points.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18) #error, new.plot not called, should output a legend at the bottom right. Output would explain colors of points.
color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow') #if the yearly rating is above the median rating, color returns as orange. Else, the color returns as yellow.
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") #plots the cocoa percent and review date for Germany. Using the above code "color3" as the colors of the points
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18) #error, new.plot not called, should output a legend at the bottom right. Output would explain colors of points.
```
##2.
One way I would improve the plots is to add a working legend. The current code for a legend does not work but if it did it would greatly improve on how the graph is interpreted. Another way to see more plots clearly is to see if points are above the average of the company location rather the median. This would be done by altering the "color_" lines and replacing "median()" with "mean()". Using a boxplot also would suffice for understanding the data more clearly. This is done by replacing "plot()" with "boxplot()".

##3.
```{r, eval=FALSE}
hist(recent_rating$Review.Date)
```
The number of ratings are a normal distrubution from 2012-2017. There are siginificantly less reviews for 2017, this could affect average rating of some certain types of cocao.

##4
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```
```{r}
cocoa$average <- by(cocoa$Rating)
```

##5
What company has the highest average rating?