---
title: "team"
author: "Joel Von Behren"
date: "10/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

The General Social Survey (GSS) has been run by NORC every other year since 1972 to keep track of current opinions across the United States. We are working with an excerpt of the dataset that covers years 1972 to 2016. The variable names along with a brief description are as follows: 

| Variable      | Description   |    
| ------------- |:-------------:| 
| Year          | Year for this respondent | 
| Age           | Age of respondent | 
| Sex           | Sex of respondent     | 
|....           | .....      | 

Now it's important to understand what each column stands for. You can find a codebook with explanations for each of the variables at https://gssdataexplorer.norc.org/

## Data Cleaning 

Initial exploration revealed that some data processing was needed before we could proceed with further visualization. All missing values were encoded with 'NA' as follows:

```{r}
library(classdata)
happy[ happy == "IAP" ] <- NA #replaces values in PolViews that are "IAP" to NA
happy[ happy == "DK" ] <- NA #replaces values in PolViews that are "DK" to NA
happy[ happy == "NA" ] <- NA #replaces values in PolViews that are "NA" to NA
sum(is.na(happy)) #finds how many variables were replaced with NA
```
In total there were `36391` number of missing values for the following `7` variables. 


Variables were also cast into the correct type in order to ease data visualization. This was done by:
```{r}
library(classdata)
happy[ happy == "89 OR OLDER" ] <- 89
happy$age <- as.numeric(as.character(happy$age))
class(happy$age)
```
This was done to change age from a character type to a numeric type. The rest of the variables are the correct type.


Factors were also organized into meaningful order as follows: 
```{r,eval=FALSE}
happyhap= happy[order(happy$happy),]
ggplot(happyhap, aes(happy)) + geom_bar() + labs(title = "Distribution of happiness", 
  x = "Types of Happiness", 
  y = "Count", 
  color = "happy")
```

The following code shows a bar graph for the factors of happiness.

```{r,eval=FALSE}
library(ggplot2)
happysex = happy[order(happy$sex),]
ggplot(happysex, aes(sex)) + geom_bar() + labs(title = "Distribution of sex", 
  x = "Sex", 
  y = "Count", 
  color = "sex")
```

The following code shows a bar graph for the factors of sex.


```{r,eval=FALSE}
library(ggplot2)
happymar= happy[order(happy$marital),]
ggplot(happymar, aes(marital)) + geom_bar() + labs(title = "Distribution of marital status", 
  x = "Types of marital status", 
  y = "Count", 
  color = "marital status")
```

The following code shows a bar graph for the factors of marital status.


```{r,eval=FALSE}
library(ggplot2)
happydeg = happy[order(happy$degree),]
ggplot(happydeg, aes(degree)) + geom_bar() +labs(title = "Distribution of Educational degrees", 
  x = "Types of degrees", 
  y = "Count", 
  color = "degree")
```

The following code shows a bar graph for the factors of the education degree obtained.


```{r,eval=FALSE}
library(ggplot2)
happyfin = happy[order(happy$finrela),]
ggplot(happyfin, aes(finrela)) + geom_bar() + labs(title = "Distribution of financial status", 
  x = "Types of financial statuses", 
  y = "Count", 
  color = "Finrela")
```

The following code shows a bar graph for the factors of financial status.


```{r,eval=FALSE}
library(ggplot2)
happyhealth =happy[order(happy$health),]
ggplot(happyhealth, aes(health)) + geom_bar() + labs(title = "Distribution of Health", 
  x = "Types of Health", 
  y = "Count", 
  color = "health")
```

The following code shows a bar graph for the factors of health status.


```{r,eval=FALSE}
library(ggplot2)
happypart = happy[order(happy$partyid),]
ggplot(happypart, aes(partyid)) + geom_bar() + labs(title = "Distribution of partyid", 
  x = "Types of party ID's", 
  y = "Count", 
  color = "partyid")
```

The following code shows a bar graph for the factors of party ID.


```{r,eval=FALSE}
library(ggplot2)
happypol = happy[order(happy$polviews),]
ggplot(happypol, aes(polviews)) + geom_bar() + labs(title = "Distribution of political views", 
  x = "Types of political views", 
  y = "Count", 
  color = "polview")
```

The following code shows a bar graph for the factors of political views.


## Data Exploration 

Two variables of interest are `...` and `...`. Their distributions are as follow: 
```{r}
#insert relevant R code here
#include graphics. DESCRIBE your plot in context. Make sure it includes axis labels and appropriate title. 
```

The distribution for `...` is `....`, suggesting that `....` 
